Automated Topic Naming

### 2012-01-19 ese/ese.tex
- [X] Fig 8 needs more explanation of how it should be read. For       example, what do values in each quadrant mean? For instance,       morjan in the top right means that s/he commits on many topics       and matches the global distribution. This implies that..

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global distribution.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/author-distance-from-aggregate}
  \caption{PostgreSQL Author Similarity to the Global Distribution of NFR topics}
\label{fig:authorsim}
\end{figure}

>>>>

% NEIL --> Explain the reason why this sentence is included: 
%It should be noted that much of PostgreSQL development originates from
%the project mailing list, and the developers are often pushing integrations. 
If we compare the global NFR distribution (that is, the relative global frequency of each NFR label)
to each author we find that 25\%
 of the authors have a similarity (Pearson correlation) of $0.47$ or less. In other words, for these authors (gathered to the lower left of Figure  \ref{fig:authorsim}),
 their NFR distribution does not match well with the global
 distribution.
Authors \texttt{momjian} and \texttt{tgl} are in the top right of
Figure \ref{fig:authorsim}
    top right, dominate in topic count and commit count, thus they are
    very similar to the global distribution of NFR topics.
Figure \ref{fig:authorsim} demonstrates that although a  few authors dominate in
the number of commits many authors exhibit different behaviour in
terms of the NFR-relevant topics of their commits. Furthermore there
are no authors in the top left corner, indicating that the authors who
commit less, do not contribute with a similar NFR-topic distribution
as \texttt{momjian} or \texttt{tgl}.
We found that number of commits correlated with an author's similarity to the
global NFR distribution ($0.59$ Pearson), i.e., the variables ``number of topics associated with a developer'' and ``number of commits'' are not discriminative.

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/author-distance-from-aggregate}
  % \caption{PostgreSQL Author Similarity to the Global Distribution of
  %   NFR topics versus Commits}
  \caption{Author commit count versus the similarity of the NFR
    distribution of an Author to the Global Distribution of NFR
    topics. Similarity is Pearson correlation between the counts of
    NFR relevant topics associated with an Author and the total counts
    of NFR relevant topics. }
\label{fig:authorsim}
\end{figure}
